---
title: "STATISTICAL INFERENCE_WEEK 4 PROJECT"
author: "kuna Abhinav 190909072"
date: "2022-10-05"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The purpose of this data analysis is to investigate the exponential distribution
and compare it to the Central Limit Theorem.


## Simulations
Set the simulation variables
```{r}
ECHO=TRUE
set.seed(1337)
lambda = 0.2
exponentials = 40
```

Run Simulations with variables
```{r}
simMean = NULL
for (i in 1 : 1000) simMean = c(simMean, mean(rexp(exponentials, lambda)))
```


## Sample Mean versus Theoretical Mean
#### Sample Mean
Calculating the mean from the simulations 
```{r}
mean(simMean)
```

#### Theoretical Mean
The theoretical mean of an exponential distribution is lambda^-1.
```{r}
lambda^-1
```

#### Comparison
There is only a slight difference between the simulations sample mean and the 
exponential distribution theoretical mean.
```{r}
abs(mean(simMean)-lambda^-1)
```


## Sample Variance versus Theoretical Variance
#### Sample Variance
Calculating the variance from the simulation means with give the sample
variance.
```{r}
var(simMean)
```

#### Theoretical Variance
theoretical variance of exponential distribution  
(lambda * sqrt(n))^-2.
```{r}
(lambda * sqrt(exponentials))^-2
```

#### Comparison between Sample and Theoretical Variance
There is only a slight difference between the simulations sample variance and 
the exponential distribution theoretical variance.
```{r}
abs(var(simMean)-(lambda * sqrt(exponentials))^-2)
```


## Distribution using a Density Histogram
This is a density histogram of the 1000 simulations. There is an overlay with a 
normal distribution that has a mean of lambda^-1 and standard deviation of 
(lambda*sqrt(n))^-1, the theoretical normal distribution for the simulations.
```{r}
library(ggplot2)
ggplot(data.frame(y=simMean), aes(x=y)) + 
  geom_histogram(aes(y=..density..), binwidth=0.2, fill="yellow", 
                 color="black") +
  stat_function(fun=dnorm, arg=list(mean=lambda^-1, 
                                    sd=(lambda*sqrt(exponentials))^-1), 
                size=2) +
  labs(title="Plot of the Simulations", x="Simulation Mean")
```{r}
