---
title: "ToothGrowth"
author: "kuna abhinav 190909072"
date: "2022-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# AVERAGE LENGTH GROWTH

Lets see Average Length Growth first

```{r,figalign='center',fig.cap="Mean of the Teeth Growth per type",fig.height=3.5,fig.width=4}
library(ggplot2)
toothgrowth <- ToothGrowth
mean.len <- with(toothgrowth,tapply(len, supp, mean))
type <- c("OJ","VC")
avg.data <- data.frame(avg=mean.len,type=type)
gd <- ggplot(avg.data,aes(x=type,y=avg)) + geom_bar(aes(fill=type),stat = 'identity') + 
ylab("Average Length Grown")+ geom_text(aes(label=avg), position=
position_dodge(width=0.9), vjust=-0.25) + ggtitle("Average Growth of Tooth Length")
gd
```
 
\newpage

```{r,fig.align='center',fig.height=5.5,fig.width=6}
ggplot(ToothGrowth,aes(x=supp,y=len)) + geom_boxplot(aes(fill=supp)) + facet_grid(.~dose) + 
  ggtitle("Boxplot for Toothgrowth with dose ")
```
So the Box Plot shows that as concentration of dose increases Tooth Growth also increases.

# Hypothesis
There are two features in this dataset on which Hypothesis Testing can be performed:
1) Hypothesis Test on "supp" i.e supplement type
2) Hypothesis Test on the "dose"

## Hypothesis Test on "supp"

Let our Null Hypothesis be that there is no difference in toothgrowth due to supplement type. 

**Null:** Toothgrowth due to "OJ" = Toothgrowth due to "VC" 

**Alternative:** Toothgrowth due to "OJ" > Toothgrowth due to "VC"
```{r}
oj.data <- subset(ToothGrowth,supp=="OJ")
vc.data <- subset(ToothGrowth,supp=="VC")
t.test(x=oj.data$len,y=vc.data$len,alternative='greater',var.equal=FALSE,paired=FALSE)
```
So, the p-value is 0.03 which is less than alpha=0.05 (Type I error rate) so we reject the null hypothesis, which means that supplement type "OJ" gives better Toothgrowth than the supplement type "VC".
## Hypothesis Test on Dosage
**Null Hypothesis:** Toothgrowth does not change with the concentration of dose

**Alternative Hypothesis:** Toothgrowth due to "OJ" > Toothgrowth increases with concentration of dose

```{r}
dose1 <- subset(ToothGrowth,dose=="0.5")
dose2 <- subset(ToothGrowth,dose=="1")
dose3 <- subset(ToothGrowth,dose=="2")
```

**First dose of 0.5mg+1mg**
```{r}
t.test(x=dose1$len,y=dose2$len,alternative="less",paired=FALSE,var.equal=FALSE)
```
So p-value is 6.342e-08 which is very less than alpha=0.05 so we reject the null hypothesis,this means that growth for dose of 0.5mg is less than that for dose of 1mg. 

**First for dose of 1mg+2mg**
```{r}
t.test(x=dose2$len,y=dose3$len,alternative="less",paired=FALSE,var.equal=FALSE)
```
The p-value is 9.532e-06 again it is very less than alpha=0.05 so we reject the null hypothesis,this means growth for dose of 1mg is less than that for 2mg.

# Assumptions taken in consideration and conclusions
1)Variance between supplement types and dose is not equal. 

2)The Data is non-paired i.e experiments are done on different subjects for each supp and dose. 

3)The variables are independent and identically distributed.

4)Supplement type "OJ" gives better Toothgrowth than the supplement type "VC". 

5)Toothgrowth increases as the concentation increases. 